---
title: "Week 2 - Thursday"
author: "Collin Stratton"
date: "1/13/2022"
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Load Libraries
```{r libs}
library(lpbrim)
library(bipartite)
```

## Data
The data for this project was gathered from myself and my friends and our favorite movie franchises. Between the 5 franchises chosen, if any of us liked a movie in the franchise, they would get a 1, otherwise they were given a 0.
```{r data}
set.seed(100)
data_matrix <- cbind(c(1, 1, 0, 1, 0), c(0, 0, 0, 1, 1), c(0, 1, 1, 0, 0), c(1, 0, 1, 0, 0), c(0, 0, 1, 1, 0))
data_matrix <- matrix(data_matrix, 5, 5)

colnames(data_matrix) <- c("Collin", "Michael", "Micah", "Rylin", "Cason")
rownames(data_matrix) <- c("Star Wars", "Marvel", "Lord of the Rings", "Maze Runner", "DC")

print(data_matrix)
```
## Brim
Make a brim module through 10 iterations
```{r brim}
set.seed(101)
module <- findModules(
    M = data_matrix,
    iter = 10,
    sparse = F
)
```

## Plot
Plot the module graph shown above with frames
```{r plot1}
plotModules(module)
```

## Analysis
Degree\n
Calculate degrees using column and row sums in R, that is, the number of connections for each vertex
```{r analysis}
friendDegrees <- colSums(data_matrix)
print(friendDegrees)
franchiseDegrees <- rowSums(data_matrix)
print(franchiseDegrees)
```

Max Degree\n
The max degree is calculated to show the maximum number of connections for a single node in the graph
```{r max_degree}
maxDegree <- max(friendDegrees, franchiseDegrees)
print(maxDegree)
```
